---
title: "p8105_hw6_cw3555"
author: "Eunice Wang"
date: '`2023-12-02`'
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load key packages.

```{r}
library(tidyverse)
library(modelr)
library(p8105.datasets)

set.seed(1)
```

### Problem 1

#### Load and clean the raw data.

```{r}
homicide_df=
  read_csv("data/homicide-data.csv") |> 
  janitor::clean_names() |> 
  mutate(
    city_state=str_c(city,state,sep =", "),
    resolved = as.numeric(disposition == "Closed by arrest"), 
    victim_age=as.numeric(victim_age)
    )|> 
      filter(!city_state %in% c("Dallas, TX","Phoenix, AZ", "Kansas City, MO", "Tulsa, AL" )) |> 
      filter(victim_race %in% c("Black", "White")) |> 
  select(city_state,resolved, victim_age, victim_sex, victim_race)
```

#### Fit a logistic regression for Baltimore, MD and save the results for estimates

```{r}
fit_baltimore=
  homicide_df |> 
  filter(city_state=="Baltimore, MD") |> 
  glm(
    resolved ~ victim_age + victim_sex + victim_race, 
    data = _, 
    family = binomial())

baltimore_results=
fit_baltimore |> 
  broom::tidy() |> 
  mutate(
    OR = exp(estimate),
    OR_CI_lower = exp(estimate-1.96*std.error),
    OR_CI_upper = exp(estimate+1.96*std.error)
    ) |> 
  filter(term=="victim_sexMale") |> 
  select(OR,OR_CI_lower,OR_CI_upper) 
```

The estimated proportion of unsolve homicides in Baltimore, MD is `r pull(baltimore_results,OR)`and the CI is [`r pull(baltimore_results,OR_CI_lower)`, `r pull(baltimore_results,OR_CI_upper)`]


#### Fit a logistic regression for each of the cities and save the results for estimates

```{r}
city_glm_model=
  homicide_df |> 
  nest(df = -city_state) |> 
  mutate(
    models = map(df, \(df) glm(resolved ~ victim_age + victim_sex +victim_race, family = binomial(), data = df)),
    results = map(models, broom::tidy)
  ) |>
  select(city_state, results) |> 
  unnest(results) |> 
  mutate(
    OR = exp(estimate),
    OR_CI_lower = exp(estimate-1.96*std.error),
    OR_CI_upper = exp(estimate+1.96*std.error)
    ) |> 
    filter(term=="victim_sexMale") |> 
    select(city_state,OR,OR_CI_lower,OR_CI_upper) 

city_glm_model |> 
  head() |> 
  knitr::kable(digits = 2) 
```

#### Create a plot that shows the estimates for each city and comment

```{r}
city_glm_model |>  
  ggplot(aes(x=fct_reorder(city_state, OR), y=OR, ymin=OR_CI_lower, ymax=OR_CI_upper))+
  geom_point()+
  geom_errorbar()+
  theme(axis.text.x=element_text(angle=90, vjust=0.5,hjust=1))+
  labs(
    x="City_State",
    y="Adjuested Estimated Odds Ratio" ,
    title="The estimated ORs and CIs for each city"
  )
```

The plots shows the estimated ORs and CIs for each city. The estimated odds ratio is ordered from the smallest estimated OR to the largest one. In most cities, the estimated odds ratio is less than 1. CIs in most cities are narrow and do not contain 1, which implies a significant difference in resolved rates between both sexes after adjustment.


